Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-03-18 manuscript/ms.tex
Updated some figures to pdf format

\begin{figure}[tb]
    \includegraphics[width=1.0\columnwidth]{seqid_dist/seqid_dist}

@@

\begin{figure}[tb]
    \includegraphics[width=1.0\columnwidth]{rmsddist/rmsddist2}

@@

% \subfloat[Src]{\label{figure:src-distances}%
%    \includegraphics[width=0.45\textwidth]{residue_pair_distances/src/distances}
% }
% \subfloat[Abl1]{\label{figure:abl-distances}%
%    \includegraphics[width=0.45\textwidth]{residue_pair_distances/abl/distances}
% }

    \includegraphics[width=1.0\columnwidth]{residue_pair_distances/src_abl_combined/distances}

@@

\begin{figure*}[h]
    \includegraphics[width=0.5\textwidth]{loopmodel_analysis/nmissing_resis_distributions}
    \caption{{\bf Distributions for the number of missing residues for templates for which remodeling (with the {\tt loopmodel} command) was either successful or unsuccessful.}
    The plotted distributions are smoothed using kernel density estimation, and the raw data points are shown as a rug plot.
    }
    \label{si:loopmodel-nmissing-residues}
\end{figure*}

>>>>

\begin{figure}[tb]
    \includegraphics[width=1.0\columnwidth]{seqid_dist/seqid_dist.pdf}

@@

\begin{figure}[tb]
    \includegraphics[width=1.0\columnwidth]{rmsddist/rmsddist2.pdf}

@@

    \includegraphics[width=1.0\columnwidth]{residue_pair_distances/src_abl_combined/distances.pdf}

@@

\begin{figure*}[h]
    \includegraphics[width=0.5\textwidth]{loopmodel_analysis/nmissing_resis_distributions.pdf}
    \caption{{\bf Distributions for the number of missing residues for templates for which remodeling (with the {\tt loopmodel} command) was either successful or unsuccessful.}
    The plotted distributions are smoothed using kernel density estimation, and the raw data points are shown as a rug plot.
    }
    \label{si:loopmodel-nmissing-residues}
\end{figure*}
